Efficient Machine Learning in a Memristor Network

### 2025-04-09 paper/paper.tex
Preparing graphs to show and proove ......
General graph found - working also for regression it seems.

@@

To generalize the training objective to a more general objective, we consider memrisotr networks with bigger networks with different topologies. Physically, reaching a desired input-output voltage mapping in a general electric circuit can be useful to adress desired voltage outputs in specific points of the circuit for variuous electronic purpuses.

>>>>

Applications of PNN have been explored in fields ranging from optics\cite{}, to electronics\cite{}
and to fluidic and mecanical systems\cite{}, amongs others.

@@

To generalize the training objective to a more general objective, we consider memrisotr networks with bigger networks with different topologies. Reaching a desired input-output voltage mapping in a generic electric circuit can be useful to adress desired voltage outputs in specific points of the circuit for variuous electronic purpuses.
